Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-10-27 ltx/first_order_framework/LaTeX_Manuscript.tex
added hinton diagrams for sensors parameters

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure10.pdf}
\end{center}
\caption{{\bf Examples of the actual and estimated neural fields and the error}. (\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data. (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. (\textbf{C}) The absolute error between the true and reconstructed fields. The error shows high frequency behaviour.}
\label{fig:Figure10}
\end{figure*}
\section*{Tables}

>>>>

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure10.pdf}
\end{center}
\caption{{\bf Examples of the actual and estimated neural fields and the error}. (\textbf{A}) The actual field at a single time instant from the full neural field model that was used to generate the data. (\textbf{B}) The reconstructed field of the reduced model, showing the effect of the basis function decomposition on the frequency content of the estimated field. (\textbf{C}) The absolute error between the true and reconstructed fields. The error shows high frequency behaviour.}
\label{fig:Figure10}
\end{figure*}

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure11.pdf}
\end{center}
\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}. Log of the RMSE of the kernel for different values of $\nu_{cm}$ and $\Delta_y$. Mean kernel estimates are obtained over 50 realisations in each case.}
\label{fig:Figure11}
\end{figure*}

\begin{figure*}[!ht]
\begin{center}
\includegraphics{./Graph/pdf/Figure12.pdf}
\end{center}
\caption{{\bf Hinton diagram of the RMSE of the kernel estimates}. Log of the RMSE of the kernel for different values of firing thereshold, $v_0$ and the slope of the sigmoid, $\varsigma$. Mean kernel estimates are obtained over 50 realisations in each case. red crosses indicate cases where the kernel can not be estimated due to numerical issues.}
\label{fig:Figure12}
\end{figure*}

\section*{Tables}
